### 2017-07-13 src/5_3_Proposal.tex
elsevier 2016 journal.tex and intro.tex revised

\chapter{Intraday Forex rates forecasting using an online cointegration approach}

High frequency forex rates 
Vector error correction model (VECM) parameters are commonly obtained using the
ordinary least squares method. Since this parameters could be sensitive to the
data, this proposal is to get these parameters using ridge regression which
could lead to a better generalization capability. In order to give with a
real-time response, an online version of VECM (OVECM) is proposed. OVECM solves
VECM considering only a sliding window of historical data and therefore
better response times could be achieved.

@@

VECM introduces the long-run relationship among a set of cointegrated variables
as an error correction term. VECM is a special case of the vector autorregresive
model (VAR) model. VAR model expresses future values as a linear combination of
variables past values.  However, VAR model cannot be used with non-stationary
variables, which is a common feature of financial assets. VECM is a linear model
but in terms of variable differences. If cointegration exists, variable
differences are stationary and they introduce an error correction term which
adjusts coefficients to bring the variables back to equilibrium. In finance,
many economic time series turn to be stationary when they are differentiated and
cointegration restrictions often improves forecasting~\cite{duy1998}. Therefore,
VECM has been widely adopted.

Both VECM and VAR model parameters are obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to errors on input data
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

@@

%The next sections are organized as follows: section~\ref{sec:background}
%presents the VAR and VECM, the OVECM algorithm proposed is presented in
%section~\ref{sec:methodology}. Section~\ref{sec:results} gives a description of
%the data used and the tests carried on to show accuracy and time comparison of
%our proposal against the traditional VECM and
%section~\ref{sec:conclusions} includes conclusions and a proposal for future
%tudy.

>>>>

\chapter{A Regularized Time Varying Vector Error Correction Model}
Vector error correction model (VECM) parameters are commonly obtained using the
ordinary least squares method (OLS). Since these parameters could be very
sensitive to the data, this proposal explores the use of ridge regression (RR)
and the agregating algorithm for regression (AAR) which could lead to a better
generalization capability. In the previous chapter OVECM was presented, which is
an online version of the traditional VECM (Vector Error Correction) that uses
OLS to get the model parameters. In this chapter a variation of OVECM is
presented. RR and AAR will be used instead of OLS to get the model parameters in
an online way.

@@

Traditionally VECM parameters are obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to errors on input data
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

@@
